Concurrent Programming with CXL

### 2020-05-17 book/paper.tex
Working on progress property

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: when nobody is in the
critical section, then any process should be able to move forward and
enter the critical section.  We call this \emph{progress}.

>>>>

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: when no process is in the
critical section, then any process that tries should be able to
enter the critical section.  We call this \emph{progress}.
